---
title: "Lab 5"
author: "Drew Hoffman, Tanner Ball, Burke Parent, David Washburn, Brandon Nelsen"
date: "9/27/2019"
output: html_document
---

```{r}
# Load tidyverse
library(tidyverse)

# Load and view the data
milk <- read.csv('state_milk_production.csv')
head(milk)

# Add a column for millions of milk pounds
milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)
```

**Team Section:**

**Arizona, California, Colorado, Illinois, and Texas**

```{r, echo=FALSE}
milksub <- milk %>%
  filter(state %in% c('Arizona','California','Colorado','Illinois','Texas')) %>%
  select(state, year, milk_million)

milkavg <- milk %>% select(year, milk_million) %>% group_by(year) %>% summarise(avg = sum(milk_million)/50)

ggplot() +
  geom_point(data = milksub, aes(x = year, y = milk_million, color = state)) + 
  ggtitle('Pounds of milk over time by state') +
  xlab('Year') +
  ylab('Milk Produced (Million lb)') +
  geom_smooth(data=milkavg, aes(x=year, y=avg), color='black')
```

**Information That the Plot Conveys:**

```{r, echo = FALSe}
ggplot(data = milk, aes(x = as.factor(year), y = (milk_million), fill = as.factor(year), width = .25)) +
  geom_col()+coord_flip() + ylab('Milk, Millions of Pounds') + xlab('Year') + labs(fill = 'Year by Color')
```
Year of most milk production: The year in which the most milk was produced was 2017, as shown by the bar shart below. The chart shows the total milk produced in millions of pounds for each year.

Year of least milk production: The year in which the least amount of milk was produced is 1975, as shown by the graph.

2017 5 states with most milk:

2017 5 states with least milk:

**Individual Sections**

**Drew:**

```{r, echo=FALSE}

```

<<<<<<< Updated upstream
**Brandon:**

```{r, echo=FALSE}

```

**David:**

```{r, echo=FALSE}

```

**Tanner:**

```{r, echo=FALSE}
test
```

**Burke:**

```{r, echo=FALSE}
library(tidyverse)

milk <- read.csv('state_milk_production.csv')

milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)

milk1999 <- milk %>%
  filter(year == 1999)
head(milk1999)

ggplot(data = milk1999, aes(x = milk_million)) +
  geom_density() + 
  ggtitle('Estimated Distribution of Milk Production, 1999')+
  xlab('Pounds of Milk, Millions')+
  ylab('Density')

summarize(milk1999,overall_mean = mean(milk_million, na.rm = TRUE), overall_median = median(milk_million, na.rm = TRUE))
```

**Most helpful thing:**


**Ethical Analysis**

=======
```{r, echo = FALSE}
library(tidyverse)

milk <- read.csv('state_milk_production.csv')

milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)

milk1999 <- milk %>%
  filter(year == 1999)
head(milk1999)

ggplot(data = milk1999, aes(x = milk_million)) +
  geom_density() + 
  ggtitle('Estimated Distribution of Milk Production, 1999')+
  xlab('Pounds of Milk, Millions')+
  ylab('Density')

summarize(milk1999,overall_mean = mean(milk_million, na.rm = TRUE), overall_median = median(milk_million, na.rm = TRUE))
```
>>>>>>> Stashed changes
